Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-24 manuscript/manuscript.tex
Shrinked Theory in manuscript

According to \citet[p.~390]{Hildebrand1987}, we can approximate any 
integral in the interval $[-1, 1]$ using a $N$th order GLQ, i.e. by a 
weighted sum of the integration kernel evaluated on the roots of the 
$N$th Legendre polynomial:

\begin{equation}
    \int\limits_{-1}^1 f(x) dx \approx \sum_{i=1}^N W_i f(x_i),
\end{equation}

\noindent where $x_i$ are the roots of the $N$th Legendre polynomial 
$P_N(x)$ and $W_i$ are the weights of each term:

\begin{equation}
    W_i = \frac{2}{(1-x_i^2)[P_N^\prime(x_i)]^2},
\end{equation}

\begin{equation}
    P_N(x_i) = 0, \quad \forall i = {1,\dots,N}.
\end{equation}

In case of an integration defined on a arbitrary interval, e.g. 
$[a,b]$, we can scale the nodes and perform a similar approximation:

\begin{equation}
    \int\limits_a^b f(x) dx \approx \frac{b-a}{2} \sum_{i=1}^N W_i f(x_i^s),
\label{eq:glq-scaled}
\end{equation}

\noindent where $x_i^s$ is the scaled $x_i$ root into the $[a,b]$ 
interval, also called nodes of the quadrature:

\begin{equation}
    x_i^s = \frac{b-a}{2} x_i + \frac{b+a}{2}.
\end{equation}

\noindent For example, if we use a second order GLQ, the roots of the 
$P_2(x)$ Legendre polynomial and its corresponding weights are $x_i = 
\pm 0.577350269$ and $W_i = 1$.

Our intention is to use GLQ to approximate the volume integrals from 
equations \ref{eq:tesseroid-pot}-\ref{eq:tesseroid-tensor}.
When tesseroids have variable densities, we can write the integral 
kernels as the product of a certain function $g$ and the density 
function:

\begin{equation}
    f(r', \phi', \lambda') = \rho(r') g(r', \phi', \lambda'),
\end{equation}

\noindent and then apply the quadrature to every integral corresponding 
to each spherical coordinate, obtaining a similar expression to the one 
shown by \citet{Asgharzadeh2007} and \citet{Uieda2016}:

@@

\begin{equation}
    A = 
    \frac{(\lambda_2 - \lambda_1)(\phi_2 - \phi_1)(r_2 - r_1)}{8}.
\end{equation}

>>>>

According to \citet[p.~390]{Hildebrand1987}, we can approximate each 
integral on equations \ref{eq:tesseroid-pot}, \ref{eq:tesseroid-grav} 
and \ref{eq:tesseroid-tensor} by applying a $N$th order GLQ, i.e. as 
a weighted sum of the integration kernel evaluated on the roots of the 
$N$th Legendre polynomial.
In the variable density tesseroid case the GLQ is applied in a similar 
way as \citet{Asgharzadeh2007} and \citet{Uieda2016} do, but in this 
scenario the density function must be also evaluated on the quadrature 
nodes:

@@

\begin{equation}
    A = 
    \frac{(\lambda_2 - \lambda_1)(\phi_2 - \phi_1)(r_2 - r_1)}{8},
\end{equation}

\noindent $(r_i, \phi_j, \lambda_k)$ are the GLQ nodes and $W_i^r$ are 
the quadrature weights \citep[see their definitions 
on][]{Hildebrand1987}.
